### 2023-06-09 resilience-safe-down.tex
up

>>>>

Without the [] hypothesis, the problem becomes undecidable. Indeed, zero-is-a-home-state problem
(asking whether zero is a home state) is undecidable for Reset Petri-nets, where it is a particular case of resilience with $\Safe = \downarrow \Safe$, $\Bad = \uparrow \Bad$. This stems from the fact that zero-is-a-home-state problem is undecidable for Minsy machines [with more than one counter,].
